%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


\cvsubsection{Research Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Givens Associate} % Job title
    {Argonne National Laboratory} % Organization
    {Lemont, IL} % Location
    {Summer 2023, 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Awarded the Givens internship for the both the summer of 2023 and 2024.}
        \item {Worked with Ahmed Attia on the development of the open source python
        package PyOED, which is an optimal experimental design package with a backend
        agnostic, extensible, data assmimilation framework.}
        \item {Began and completed research leveraging a new stochastic framework for
        optimal experimental design to tackle the robust optimal experimental design
        problem for non-linear inverse problems.}
        \item {Culminated in five talks given by me (Two at the SASSy seminar at
        Argonne, one at SIAM UQ24, two planned at SIAM MDS24 and SIAM CSE25 respectively).}
        \item {Culminated in three papers (one published, one in submission, one in
        mid-research)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {North Carolina State University} % Organization
    {Raleigh, NC} % Location
    {Aug. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Hired as a research assistant for Alen Alexanderian via NSF Grant DMS-2111044.}
        \item {Generally working in the field of Bayesian inverse problems, and their sensivity analysis and optimal experimental design formulation.}
        \item {Developed a novel technique for differentiating the information gain of a linear Bayesian inverse problem with respect to the model hyperparameters.}
        \item {Culminated in a talk at SIAM CSE23 and a paper.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Research Assistant} % Job title
    {Ohio State University} % Organization
    {Athens, OH} % Location
    {June. 2019 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Joined a research team udner professor Qiliang Wu, and co-researcher Mason Haberle in researching the field of pattern formation}
        \item {Proved the nonlinear stability of the 2D Swift-Hohenberg equation at the zigzag boundary.}
        \item {Paper in submission with a published preprint.}
      \end{cvitems}
    }

\end{cventries}

\cvsubsection{Teaching Experience}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Teaching Assistant} % Job title
    {North Carolina State University} % Organization
    {Raleigh, NC} % Location
    {Aug. 2020 - Aug 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Taught recitation sections for the department of mathematics and North Carolina State. In particular, taught Calculus I in the fall of 2020, and Calculus II in the spring and summer of 2021.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Teaching Assistant} % Job title
    {New York University} % Organization
    {New York, NY} % Location
    {Sep. 2017 - May 2019 and Spring 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Tutored and graded for undergraduate numerical computing in Spring 2020.}
        \item {Taught tutoring sessions and graded for graduate fundamental algorithms in
          fall 2017 and 2018.}
        \item {Taught tutoring sessions and graded for undergraduate basic algorithms in
          spring 2018 and 2019.}
      \end{cvitems}
    }

\end{cventries}

\cvsubsection{Service}

\cventry
    {Organizer} % Job title
    {Applied Math Graduate Student Seminar} % Organization
    {Raleigh, NC} % Location
    {Aug. 2022 - Now} % Date(s)
    {}

\cventry
    {On the EBoard} % Job title
    {Student Association of Comptuing @ New York University} % Organization
    {New York, NY} % Location
    {2017 - 2020} % Date(s)
    {}
